correlationstuff

### 2024-01-27 corstuff.Rmd
some new stuff

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR","PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

@@

#print.psych(kahan.fa, cut = 0.4, sort = TRUE)

@@

rename_map <- c(
  "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
  "K_HEQUAL" = "(H)We have gone too far in pushing equal rights in this country.",
  "K_ERADEQ1" = "(E)We need to dramatically reduce inequalities between the rich and the poor.",
  "K_EWEALTH" = "(E)Our society would be better off if the distribution of wealth was more equal.",
  "K_ERADEQ2" = "(E)We need to dramatically reduce inequalities between men and women."
)

@@

@@

# 4) lm with ecopolvars 
m1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + KahanS + KahanH , data = fascale_scores)

>>>>

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_H","K_I","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR","PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

@@

print.psych(kahan.fa, cut = 0.4, sort = TRUE)

@@

flex <- function(data, title=NULL) {
  # this grabs the data and converts it to a flextbale
  flextable(data) %>%
  # this makes the table fill the page width
  set_table_properties(layout = "autofit", width = 1) %>%
  # font size
  fontsize(size=11, part="all") %>%
    #this adds a ttitlecreates an automatic table number
      set_caption(title, 
                  autonum = officer::run_autonum(seq_id = "tab", 
                                                 pre_label = "Table ", 
                                                 post_label = "\n", 
                                                 bkm = "anytable")) #%>%
  # font type
  #font(fontname="Times New Roman", part="all")
}

rename_map <- c(
  "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
  "K_HEQUAL" = "(H)We have gone too far in pushing equal rights in this country.",
  "K_ERADEQ1" = "(E)We need to dramatically reduce inequalities between the rich and the poor.",
  "K_EWEALTH" = "(E)Our society would be better off if the distribution of wealth was more equal.",
  "K_ERADEQ2" = "(E)We need to dramatically reduce inequalities between men and women.",

  "K_IINTRFER" = "(I)The government interferes far too much in our everyday lives.",
  "K_HREVDIS1" = "(H)Nowadays it seems like there is just as much discrimination against upper castes as there is against Dalits.",
  "K_EDISCRIM" = "(E)Discrimination against minorities is still a very serious problem in our society.",
  "K_IPRIVACY" = "(I)The government should stop telling people how to live their lives.",
  "K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
)

fa_table <- function(x) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
   rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")
  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(rename_map), rename_map[item], item),
      across(where(is.numeric), round, 3)
    )
}

@@

kahan.fa[["Vaccounted"]] %>%
  as.data.frame() %>%
  rownames_to_column("Property") %>%
    mutate(across(where(is.numeric), round, 3)) %>%
    flex("Eigenvalues and Variance Explained for Rotated Factor Solution")

@@

summary(m1_kahan)
# 4) lm with ecopolvars 
m1_allscales <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State+ Pdevelop + Ndevelop + KahanS + KahanH , data = fascale_scores)

summary(m1_allscales)
